RT-qPCR (Real-Time Quantitative Polymerase Chain Reaction) Analysis Report
--------------------------------------------------------------------------

Date: `r Sys.time()`
-----------------------------------------

Cq values and amplification efficiencies:
-----------------------------------------
````{r, echo=FALSE}
x <- Cq()
x.result <- x[,c("exprs","effs")]
names(x.result) <- c("Cq","Efficiency")
knitr::kable(x.result, digits = 4, format = "markdown")
````

Cq values and amplification efficiencies after replacing above cut offs by nondetects (NA):
-------------------------------------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
if (r.cutoff()== "None")
  {
  text1()
  }
if (r.cutoff()== "Replace"){
x <- Cq.cut()
x.result <- x[,c("exprs","effs")]
names(x.result) <- c("Cq","Efficiency")
knitr::kable(x.result, digits = 4)
}
````

Cq values and amplification values after replacing nondetects by user defined value:
------------------------------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
if (replace.nas()== "None"){text1()}
if (replace.nas()== "Replace"){
x <- Cq.rena()
x.result <- x[,c("exprs","effs")]
names(x.result) <- c("Cq","Efficiency")
knitr::kable(x.result, digits = 4)
}
````

Cq values and amplification efficiencies after replacing specific values:
-------------------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
if (replace.value()=="None"){text1()}
if (replace.value()=="Replace"){
x <- Cq.re()
x.result <- x[,c("exprs","effs")]
names(x.result) <- c("Cq","Efficiency")
knitr::kable(x.result, digits = 4)
}
````

Cq values and amplification efficiencies after removing the nondetects within replicates (method- mean or median):
------------------------------------------------------------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
if (n.det() == "None"){
  text2()
  }
if ((n.det()== "Mean")||(n.det()=="Median")){
x <- Cq.nd()
x.result <- x[,c("exprs","effs")]
names(x.result) <- c("Cq","Efficiency")
knitr::kable(x.result, digits = 4)
}
````

Combining technical replicates based on Cq values and S.D. of Cq values within replicates:
------------------------------------------------------------------------------------------
````{r, echo=FALSE}
x <- CqReps()
x.result <- x[,c("ID","Cq","sd.Cq")]
knitr::kable(x.result, digits = 4)
````

Combining technical replicates based on efficiencies and S.D. of Cq and efficiencies within replicates:
-------------------------------------------------------------------------------------------------------
````{r, echo=FALSE}
x <- effsReps()
x.result <- x[,c("ID","Cq","sd.Cq","effs","sd.effs")]
knitr::kable(x.result, digits = 4)
````

Delta Cq values:
-----------------------------------------
```{r, echo=FALSE}
x <- deltaCq()
x.result <- x[,c("ID","deltaCq","sd.deltaCq")]
knitr::kable(x.result, digits = 4)
```

Delta Delta Cq values and fold concentrations of target samples: 
----------------------------------------------------------------
```{r, echo=FALSE}
knitr::kable(deltadeltaCq(), digits = 4)
```

Relative expression ratio of target samples:
--------------------------------------------
````{r, echo=FALSE}
knitr::kable(NRQeffs(), digits = 4)
````


Settings used during RT-qPCR analysis:
--------------------------------------------
````{r, echo=FALSE, results='asis'}
##cat("Input file name: ", ifelse(is.null(input[["input.file"]][["name"]]), "\n\n")
cat("Select the type of PCR: ", input$pcrtype, "\n\n")
cat("Select efficiency computing method: ", input$efficiencymethod, "\n\n")
cat("Select to apply the cut off: ", input$replaceabovecutoff, "\n\n")
cat("Cq cut off: ", input$Cqcutoff, "\n\n")
cat("efficiency cut off: ", input$effscutoff, "\n\n")
cat("Select to replace the specific Cq and Eff. values: ", input$replacevalue, "\n\n")
cat("The row, where Cq value is to be replaced: ", input$Cqrow, "\n\n")
cat("New Cq value: ", input$cqvalue, "\n\n")
cat("The row, where efficiency value is to be replaced: ", input$effsrow, "\n\n")
cat("New Efficiency value: ", input$neweffs, "\n\n")
cat("Select to replace all NAs by user defined value: ", input$replacenas, "\n\n")
cat("Provide the Cq value to replace NAs: ", input$cqna, "\n\n")
cat("Provide the efficiency value to replace NAs: ", input$effsna, "\n\n")
cat("Select method to remove nondetects: ", input$nondetects, "\n\n")
cat("Select method to combine Technical Replicates: ", input$ctechreps, "\n\n")
cat("Type the name of reference gene under column 'Target Name': ", input$Reference, "\n\n")
````


Session Information:
--------------------------------------------
````{r, echo=FALSE, results='asis'}
sessionInfo("RTqPCR")
````




